---
output: github_document
---

[![Build Status](https://travis-ci.org/n8thangreen/QALY.svg?branch=master)](https://travis-ci.org/n8thangreen/CEdecisiontree)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/n8thangreen/QALY?branch=master&svg=true)](https://ci.appveyor.com/project/n8thangreen/CEdecisiontree)
[![Coverage status](https://codecov.io/gh/n8thangreen/QALY/branch/master/graph/badge.svg)](https://codecov.io/github/n8thangreen/CEdecisiontree?branch=master)
[![experimental](http://badges.github.io/stability-badges/dist/experimental.svg)](http://github.com/badges/stability-badges)


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  tidy = FALSE,
  error = FALSE,
  fig.width = 5,
  fig.height = 5
)
```
# CEdecisiontree

An R package for lightweight cost-effectiveness analysis using decision trees.

Currently contains functions to:

- matrix (wide, sparse) representation

## To do
Request welcome; please use [Issues](https://github.com/n8thangreen/CEdecisiontree/issues)

- fully integrate src


## Installing CEdecisiontree

To install the development version from github:
```{r eval=FALSE}
library(devtools)
install_github("n8thangreen/CEdecisiontree")
```

Then, to load the package, use:
```{r eval=FALSE}
library(CEdecisiontree)
```


## Motivation
xxx


## Basic example

```{r}
suppressMessages(library(CEdecisiontree))
```



See package [vignette](http://htmlpreview.github.io/?https://github.com/n8thangreen/CEdecisiontree/blob/master/inst/doc/vignette_main.html) for more details and examples.

## License

GPL-3 © 
