---
title: "A simple cost-effectiveness analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ce_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Although the `CEdecisiontree` package allows us to do calculations using different values separately, the main purpose is to carry out cost-effectiveness analyses.
This is performed calling the `dectree()` function for cost and health inputs using the wrapper `run_cedectree()`.

## Example

```{r warning=FALSE, message=FALSE}
library(CEdecisiontree)
library(purrr)
library(tibble)
```

For a single outcome type

```{r}
tree_dat <- 
  tribble(
    ~from, ~to, ~vals, ~prob, 
    1,  2,   10,   0.7, 
    1,  3,   NA,   0.3, 
    2,  4,  100,   0.1, 
    2,  5,   NA,   0.9, 
    3,  6,  100,   0.9, 
    3,  7,   NA,   0.1)
```

The function `dectree()` requires the dataframe defining the tree above.
Optionally, it can also take PSA distributions on probabilities and values, a PSA sample size `n`, and a list of groups of nodes `state_list`.
It then returns expected values for point estimates, and for PSA if supplied.
Also, pathway joint probabilities are returned if states are provided.

```{r}
dectree(tree_dat,
        state_list = list(all = c(4,5,6,7)))
```


For cost-effectiveness analysis including PSA

```{r}
# run_cedectree(tree_dat)
```


