---
title: "Scenario Sensitivity Analysis"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scenario Sensitivity Analysis}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Scenario (or deterministic) sensitivity analysis is a common part of any cost-effectiveness analysis [@Briggs2012].
Here we will carry this out for a simple decision tree.
This involves explicitly specifying values for particular branch probability and/or values and calculating the total expected value.

## Example

```{r warning=FALSE, message=FALSE}
library(CEdecisiontree, quietly = TRUE)
library(assertthat, quietly = TRUE)
library(tibble, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(purrr, quietly = TRUE)
```

We create a complete design meaning all combinations on the grid of input values.
Alternatively, we may only want to do a one-way analysis and so would set the non-varied term to some common baseline distribution or fixed value.
In our example, we will choose three values for each parameter. We can think of this as a worst-, most likely and best-case scenario.

```{r}
p <- c(NA_real_, 0.4, 0.6)

c2 <- c(10, 50, 100)
c3 <- c(5, 40, 150)

c_grid <-
  expand.grid(c2 = c2,
              c3 = c3) %>% 
  cbind(c1 = 0L, .) %>% 
  t() %>% 
  as.data.frame()

c_grid
```

Then define the decision tree structure as just a basic binary tree.

```{r}
child <- list("1" = c(2, 3),
              "2" = NULL,
              "3" = NULL)
```

We can now loop over the inputs and generate a complete tree object for each cost combination.

```{r warning=FALSE}
tree_dat_sa <- list()

for (i in seq_along(c_grid)) {
  
  tree_dat_sa[[i]] <-
    define_model(
      tree_dat =
        list(child = child,
             dat = data.frame(
               node = names(child),
               prob = p,
               vals = c_grid[[i]])
        ))
}
```

This results in a list of trees.
```{r}
tree_dat_sa[[1]]
```

Now, it is straightforward to map over each of these trees to obtain the total expected values.

```{r}
res <- map_dbl(tree_dat_sa, dectree_expected_values)
res
```

### Tornado plot

Lets create a tornado plot showing a one-way sensitivity analysis.
We'll use my `ceplot`.
By specifying the output data as a model frame it is handled appropriately.

```{r warning=FALSE, message=FALSE}
library(ceplot)
library(reshape2)
library(magrittr)
library(plyr)
library(purrr)
library(dplyr)
library(ggplot2)

sa_dat <- as.data.frame(cbind(t(c_grid), res))

sa_model_dat <- model.frame(formula = res ~ c1 + c2 + c3,
                            data = sa_dat)

##TODO: ceplot package build error
# sa_model_dat %>%
#   ceplot::create_tornado_data() %>%
#   ceplot::ggplot_tornado() 
```

