---
title: "Using function dispatch"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

So far, we have passed particular data formats to `dectree_expected_values`, where we need to be explicit about which arguments they are associated with.
Alternatively, we can define the model upfront and then pass this object to `dectree_expected_values` for it to dispatch to the appropriate function using S3.

## Example

```{r}
suppressPackageStartupMessages(library(CEdecisiontree))
suppressPackageStartupMessages(library(dplyr))
```

Let us create 3 input variables, in line with the 3 formats we have met already, using the `define_model` function.
```{r}
model_transmat <- 
  define_model(transmat =
                 list(prob = matrix(data = c(NA, 0.5, 0.5), nrow = 1),
                      vals = matrix(data = c(NA, 1, 2), nrow = 1)
                 ))
model_transmat

model_tree <- 
  define_model(tree_dat =
                 list(child = list("1" = c(2, 3),
                                   "2" = NULL,
                                   "3" = NULL),
                      dat = data.frame(node = 1:3,
                                       prob = c(NA, 0.5, 0.5),
                                       vals = c(0, 1, 2))
                 ))
model_tree

model_long <- 
  define_model(dat_long = data.frame(from = c(1, 1),
                                     to = c(2, 3),
                                     prob = c(0.5, 0.5),
                                     vals = c(1, 2)))
model_long
```

Now it is simply a case of passing this to main function call.
```{r}
dectree_expected_values(model_transmat)
dectree_expected_values(model_tree)
dectree_expected_values(model_long)
```
